### 2021-04-18 paper/ase21/abstract.tex
[ASE21] Till Conclusion

  To alleviate the problem, we propose $\tool$, a JavaScript Specification Type
  Analyzer using Refinement.  It is the first tool that performs \textit{type
  analysis} on JavaScript specifications and detects specification bugs using a
  \textit{bug detector}.  For a given specification, $\tool$ first compiles each
  abstract algorithm written in a structured natural language to a corresponding
  function in $\ires$, an untyped intermediate representation for ECMAScript.
  Then, it performs type analysis for compiled functions with specification
  types defined in ECMAScript.  Based on the result of type analysis, $\tool$
  detects specification bugs using a bug detector consisting of four checkers.
  Moreover, to increase precision of type analysis, we present
  \textit{condition-based refinement} for type analysis, which prunes out
  infeasible abstract states using conditions of assertions and branches.  We
  evaluated $\tool$ with all \inred{XXX} versions in the official ECMAScript
  repository for the recent \inred{three years from 2018 to 2021}.  Our tool
  detected \inred{XXX} specification bugs including only \inred{XXX} false
  alarms caused by the imprecision of type analysis in \inred{XX} minutes on
  average.  Among \inred{XXX} true alarms, \inred{XXX} bugs are resolved after
  existing for \inred{XXX} days on average and \inred{XX} bugs still exist in
  the latest version of ECMAScript for \inred{XXX} days.  We reported all
  \inred{XX} newly found bugs and they are confirmed by the committee.
\end{abstract}

>>>>

  To alleviate the problem, we propose $\tool$, a JavaScript Specification Type
  Analyzer using Refinement.  It is the first tool that performs \textit{type
  analysis} on JavaScript specifications and detects specification bugs using a
  \textit{bug detector}.  For a given specification, $\tool$ first compiles each
  abstract algorithm written in a structured natural language to a corresponding
  function in $\ires$, an untyped intermediate representation for ECMAScript.
  Then, it performs type analysis for compiled functions with specification
  types defined in ECMAScript.  Based on the result of type analysis, $\tool$
  detects specification bugs using a bug detector consisting of four checkers.
  Moreover, to increase precision of type analysis, we present
  \textit{condition-based refinement} for type analysis, which prunes out
  infeasible abstract states using conditions of assertions and branches.  We
  evaluated $\tool$ with all 864 versions in the official ECMAScript repository
  for the recent three years from 2018 to 2021.  Our tool took \inred{230}
  seconds on average to perform type analysis for each version, and detected
  \inred{200} type-related specification bugs with \inred{50.3}\% precision;
  \inred{91} out of \inred{200} bugs are true bugs.  Among them, \inred{14} bugs
  are newly detected by $\tool$ and the committee confirmed all of them.
\end{abstract}

### 2021-04-18 paper/ase21/intro.tex
[ASE21] Till V.B Precision
[ASE21] Till Conclusion

The correctness of ECMAScript becomes more important because an incorrect
description of syntax or semantics in the specification can lead to the wrong
implementation of existing JavaScript engines used in various fields.  However,
all the specification updates are currently manually checked by the Ecma
Technical Committee 39 (TC39) without any automated tools.  This manual checking
process is obviously labor-intensive and also error-prone thus the current
JavaScript specification is vulnerable to specification bugs.  Besides, in late
2014, the committee announced yearly release cadence and open development
process of ECMAScript to quickly adapt to an evolving development environment.
According to \citet{jiset}, the average number of updated steps of abstract
algorithms between consecutive releases from ES7 (2016) to ES10 (ES2019) is
9645.5.  In the official repository of ECMAScript, \inred{X,XXX} pull requests
and \inred{X,XXX} commits exist in the master branch.  Therefore, it makes more
difficult to manually check all the specification updates using limited human
resources.

@@

For the compiled mechanized specifications, $\tool$ performs type analysis for
compiled functions with specification types defined in ECMAScript.  ECMAScript
contains not only JavaScript language types but also specification types such as
abstract syntax trees (ASTs), internal records (i.e. environments, completions,
or property descriptors), and internal list-like structures.  Our tool extract
syntax and table-based type information from ECMAScript and constructs type
hierarchy and fields for ASTs and records.  Based on the extracted types,
$\tool$ performs type analysis and detects specification bugs using a
\textit{bug detector} consisting of four different checkers: 1) reference
checker, 2) arity checker, and 3) assertion checker, 4) operand type checker.
Moreover, to increase precision of type analysis, we also present
\textit{condition-based refinement} for type analysis on ECMAScript. Its main
concept is to prunes out infeasible abstract states by using conditions of
assertions and branches.  The refinement technique can reduce false alarms
caused by spurious types inferred by imprecise analysis.  We evaluate our tool
with all \inred{XXX} different versions existed in the official ECMAScript
repository for the recent \inred{three years from 2018 to 2021}.

In summary, our main contributions are as follows:
\begin{itemize}
  \item We present $\tool$, which is the first tool that performs \textit{type
    analysis} on ECMAScript to check the the correctness of JavaScript language
    specifications.  $\tool$ automatically detects specification bugs via the
    \textit{bug detector} consisting of four different checkers: 1) reference
    checker, 2) arity checker, and 3) assertion checker, 4) operand type
    checker.
  \item We present \textit{condition-based refinement} for type analysis of
    ECMAScript to reduce false alarms by increasing the analysis precision.  Its
    main idea is to prune out infeasible abstract states by using conditions of
    assertions and branches.
  \item We demonstrate the practicality of $\tool$. For recent \inred{XXX}
    different versions of ECMAScript, our tool detected \inred{XXX}
    specification bugs including only \inred{XXX} false alarms caused by the
    imprecision of type analysis in \inred{XX} minutes on average.  Among
    \inred{XXX} true alarms, \inred{XXX} bugs are resolved after existing for
    \inred{XXX} days on average and \inred{XX} bugs still exist in the latest
    version of ECMAScript for \inred{XXX} days.  We reported all \inred{XX}
    newly found bugs and they are confirmed by the committee.
\end{itemize}

>>>>

The correctness of ECMAScript becomes more important because an incorrect
description of syntax or semantics in the specification can lead to the wrong
implementation of existing JavaScript engines used in various fields.  However,
all the specification updates are currently manually checked by the Ecma
Technical Committee 39 (TC39) without any automated tools.  This manual checking
process is obviously labor-intensive and also error-prone thus the current
JavaScript specification is vulnerable to specification bugs.  Besides, in late
2014, the committee announced yearly release cadence and open development
process of ECMAScript to quickly adapt to an evolving development environment.
According to \citet{jiset}, the average number of updated steps of abstract
algorithms between consecutive releases from ES7 (2016) to ES10 (ES2019) is
9645.5.  In the official repository of ECMAScript, \inred{1,200} pull requests
and \inred{3,000} commits exist in the master branch.  Therefore, it makes more
difficult to manually check all the specification updates using limited human
resources.

@@

For the compiled mechanized specifications, $\tool$ performs type analysis for
compiled functions with specification types defined in ECMAScript.  ECMAScript
contains not only JavaScript language types but also specification types such as
abstract syntax trees (ASTs), internal records (i.e. environments, completions,
or property descriptors), and internal list-like structures.  Our tool extract
syntax and table-based type information from ECMAScript and constructs type
hierarchy and fields for ASTs and records.  Based on the extracted types,
$\tool$ performs type analysis and detects specification bugs using a
\textit{bug detector} consisting of four different checkers: 1) reference
checker, 2) arity checker, 3) assertion checker, and 4) operand checker.
Moreover, to increase precision of type analysis, we also present
\textit{condition-based refinement} for type analysis on ECMAScript. Its main
concept is to prunes out infeasible abstract states by using conditions of
assertions and branches.  The refinement technique can reduce false alarms
caused by spurious types inferred by imprecise analysis.  We evaluate our tool
with all \inred{864} different versions existed in the official ECMAScript
repository for the recent \inred{three years from 2018 to 2021}.

In summary, our main contributions are as follows:
\begin{itemize}
  \item We present $\tool$, which is the first tool that performs \textit{type
    analysis} on ECMAScript to check the the correctness of JavaScript language
    specifications.  $\tool$ automatically detects specification bugs via the
    \textit{bug detector} consisting of four different checkers: 1) reference
    checker, 2) arity checker, 3) assertion checker, and 4) operand checker.
  \item We present \textit{condition-based refinement} for type analysis of
    ECMAScript to reduce false alarms by increasing the analysis precision.  Its
    main idea is to prune out infeasible abstract states by using conditions of
    assertions and branches.
  \item We demonstrate the practicality of $\tool$. Our tool took \inred{230}
    seconds on average to perform type analysis for each version, and detected
    \inred{200} type-related specification bugs with \inred{50.3}\% precision;
    \inred{91} out of \inred{200} bugs are true bugs.  Among them, \inred{14}
    bugs are newly detected by $\tool$ and the committee confirmed all of them.
\end{itemize}

### 2021-04-18 paper/ase21/related.tex
[ASE21] Till Conclusion

\begin{itemize}
  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
\end{itemize}

>>>>

JavaScript specification type analysis is related to two research fields:
JavaScript tools, mechanized specification extraction, specification-based
testing.

\paragraph{JavaScript Tools}
ECMAScript is the standard language specification for JavaScript maintained by
the Ecma Technical Committee 39 (TC39).  In late 2014, the committee announced
yearly release cadence and open development process of ECMAScript to quickly
adapt to an evolving development environment.  Existing JavaScript engines, such
as Google V8~\cite{v8}, GraalJS~\cite{graaljs}, QuickJS~\cite{qjs}, and Moddable
XS~\cite{moddable}, must conform to the syntax and semantics described in
annually updated ECMAScript.  Beyond JavaScript engines, there are diverse
research directions to utilize JavaScript specifications.  Several researchers
developed static analyzers, such as TAJS~\cite{tajs}, SAFE~\cite{safe},
JSAI~\cite{jsai}, and WALA~\cite{wala}, based on abstract interpretation
framework~\cite{ai1977, ai1992} with various analysis techniques.  They defined
abstract semantics of JavaScript semantics described in ECMAScript to statically
analyze given JavaScript programs in a finite time.  \citet{jsexplain} presented
JSExplain, a debugger for JavaScript, by implementing a reference interpreter in
OCaml directly conforms to algorithm steps in ECMAScript.  For a given
JavaScript program, the debugger produces execution traces interactively
invesitgated in a browser, with an interface that displays not only the code and
the state of the interpreter.  \citet{javert} introduced JaVerT, a JavaScript
verification toolchain, based on separation logic with their own intermediate
goto language JSIL.  Moreover, JaVerT 2.0~\cite{javert2} extends it to support
compositional symbolic execution for JavaScript based on bi-abduction.  However,
all of them manually handles ECMAScript with their own intermediate
representations thus many of them still targets ES5.1, the most famous old
version of ECMAScript released in 2011, not the latest one.

\paragraph{Mechanized Specification Extraction}
Several researchers extracted mechanized specifications from specifications
written in a natural language to mechanically handle materials in
specifications.  For system architectures, researchers utilized complex Natural
Language Processing (NLP) and Machine Learning (ML) to extract formal semantics
of small-sized low-level assembly languages for x86~\cite{x86} and
ARM~\cite{arm}.  For Java API functions, \citet{javadoc} presented a technique
to automatically extract models from their documentation using NLP techniques.
Instead of specific API functions, \citet{jiset} presented $\jiset$, a tool that
extracts mechanized language specification from ECMAScript.  While previous
JavaScript formal semantics~\cite{lambdajs, jscert, kjs} were manually defined,
$\jiset$ automatically extracts formal semantics directly from ECMAScript.  We
utilized $\jiset$ to perform type analysis for diverse versions of ECMAScript in
$\tool$.

\paragraph{Specification-based Testing}
Several researchers utilized specifications to test their implementations.  For
network protocols, \citet{basespec} proposed a novel approach named
\textsc{BaseSpec}, which extracts message structures from tables in cellular
specifications for L3 protocols to perform comparative analysis with baseband
software.  \citet{spectest} presented SpecTest that utilized an executable
language semantics to perform fuzzing for Java and Solidity compilers.  For
JavaScript, \citet{comfort} presented \textsc{Comfort}, a compiler fuzzing
framework to detect JavaScript engine bugs using ECMAScript with deep
learning-based language models.  \citet{jest} extended $\jiset$ to $\jest$ that
performs $N$+1-version differential testing with a reference interpreter
extracted from ECMAScript and $N$ different JavaScript engines.  $\jest$ detects
not only engine bugs but also specification bugs in ECMAScript based on the
cross-referencing oracle.  However, it requires multiple JavaScript engines and
takes dozens of hours to cover semantics for each version of ECMAScript.
Instead, $\tool$ can detect specification bugs without JavaScript engines less
than 5 minutes.  Moreover, $\tool$ utilizes abstract semantics instead of
concrete semantics used in $\jest$ thus it can quickly cover more semantics.
